\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-04-24 paper/paper_draft.tex
paper changes

We can relate $\kappa$ and $\gamma$ directly to the lensing potential as
% TODO: should these subscripts be theta and phi?
\begin{equation}
    \kappa = \frac{1}{2}\nabla^2\psi, \quad \gamma_1 = \frac{1}{2}(\partial_{n_1}^2 - \partial_{n_2}^2)\psi, \quad \gamma_2 = \partial_{n_1}\partial_{n_2} \psi.
\end{equation}

@@

% \begin{gather*}
%     \langle \psi_{l_1m_1} \psi_{l_2m_2} \psi_{l_3m_3} \rangle = A_{\mathbf{l}}^{\mathbf{m}} (-1)^{l_1 + l_2 + l_3} 8 (2\pi)^{9/2} \int_0^{\chi_*} W(\chi, \chi_*)^3 \frac{\chi^2}{l_1^2l_2^2l_3^2} \br{\frac{3\Omega_m H^2}{2}}^3|_{\eta=\eta_0-\chi}\\
%     \quad \times B^\delta\br{ \frac{l_1}{\chi}, \frac{l_2}{\chi}, \frac{l_3}{\chi}; \eta_0-\chi } \mathrm{d}\chi, \\
%     C_l^\psi = \frac{72\pi^3}{l^4}\int_0^{\chi_*}\d \chi \chi^2(\Omega_m^2H^4)|_{\eta=\eta_0-\chi} C^\delta_{l/\chi}(\eta_0-\chi) W(\chi)^2.
% \end{gather*}

\subsection{Convergence and shear multipole moments}
\paragraph{Convergence}
% TODO: make notation of nabla nicer/more consistent

Taking the harmonic decomposition of the convergence,
\begin{equation}
    \kappa(\hat{\mathbf n}) = \kappa_{lm}Y_l^m(\hat{\mathbf n}),
\end{equation}
you can relate it to the multipole moments of the lensing potential through
\begin{equation}
    \kappa_{lm} = \frac{1}{2}(\nabla^2\psi)_{lm} = \frac{l(l+1)}{2}\psi_{lm}
\end{equation}
because the spherical harmonics are eigenfunctions of the Laplacian operator.

\paragraph{Shear}
On the other hand, the shear is given by
\begin{equation}
    \gamma = \gamma_1 + i\gamma_2 = \frac{1}{2}\eth_1(\eth_0\psi)
\end{equation}
where the spin raising operator, $\eth_s$ acts on a spin $s$ function defined on $S^2$ to create a spin $s+1$ function. The above equality is proven explicitely in appendix ... %TODO: write and cite appendix proving equivalence
$\eth_s$ can be written in $(\theta, \phi)$ coordinates as
\begin{equation}
    \eth_s = -\sin^s\theta(\partial_\theta + \frac{i}{\sin\theta})\frac{1}{\sin^s\theta}.
\end{equation}
It is worth explaining that in this context a spin $s$ function referes to a function $_sf(\theta, \phi)$ that transforms under any rotation of coordinates by picking up a phase factor $e^{is\alpha}$, with $\alpha$ the angle of the rotation, i.e.
\begin{equation}
    f'(\theta', \phi') = e^{is\alpha}f(\theta, \phi).
\end{equation}
Shear is actually a spin 2 function, which can immediately be seen by observing that rotating a galaxy image stretched and squeezed through weak lensing by $180$ degrees gives the same stretching and squeezing, i.e. the same shear. It is thus expected that the shear is proportional to $\eth^2\psi$.

The spin weighted spherical harmonics, $_sY_l^m$ are eigenfunctions of the raising/lowering operator, in particular
\begin{equation}
    \eth_sY_l^m = \sqrt{(l-s)(l+s+1)} _{s+1}Y_l^m.
\end{equation}
Decomposing the shear as
\begin{equation}
    \gamma(\theta, \phi) = \gamma_{lm} {}_sY_l^m(\theta,\phi),
\end{equation}
we thus find
\begin{equation}
    \gamma_{lm} = \frac{1}{2}\sqrt{(l-1)(l)(l+1)(l+2)} \psi_{lm}
\end{equation}

>>>>

We can relate $\kappa$ and $\gamma$ directly to the lensing potential as
\begin{equation}
    \kappa = \frac{1}{2}\nabla^2\psi, \quad \gamma_1 = \frac{1}{2}(\partial_{n_1}^2 - \partial_{n_2}^2)\psi, \quad \gamma_2 = \partial_{n_1}\partial_{n_2} \psi.
\end{equation}

It is shown in appendix \ref{sec:shear} that
\begin{equation}
    \gamma := \gamma_1 + i\gamma_2 = \frac{1}{2}\eth_1(\eth_0\psi)
\end{equation}
where the spin raising operator, $\eth_s$ acts on a spin $s$ function defined on $S^2$ to create a spin $s+1$ function.
$\eth_s$ can be written in spherical coordinates $(\theta, \phi)$ as\footnote{We use the physics convention for the definition of $\theta$ and $\phi$ here.}
\begin{equation}
    \eth_s = -\sin^s\theta(\partial_\theta + \frac{i}{\sin\theta})\frac{1}{\sin^s\theta}.
\end{equation}
In this context a spin $s$ function referes to a function $_sf(\theta, \phi)$ that transforms under any rotation of coordinates by picking up a phase factor $e^{is\alpha}$, with $\alpha$ the angle of the rotation, i.e.
\begin{equation}
    f'(\theta', \phi') = e^{is\alpha}f(\theta, \phi).
\end{equation}
Shear is thus a spin 2 function, which can be checked by noting that rotating a galaxy image stretched and squeezed through weak lensing by $180$ degrees gives the same stretching and squeezing, i.e. the same shear.

% The spin weighted spherical harmonics, $_sY_l^m$ are eigenfunctions of the raising/lowering operator, in particular
% \begin{equation}
%     \eth_sY_l^m = \sqrt{(l-s)(l+s+1)} _{s+1}Y_l^m.
% \end{equation}
The spherical harmonics are eigenfunctions of $\nabla^2$ and the spin raising and lowering operators. Using this property, the corresponding relations in spherical harmonic space can be shown to be 
\begin{equation*}
    \kappa_{lm} = \frac{l(l+1)}{2}\psi_{lm}, \quad \gamma_{lm} = \frac{\sqrt{(l-1)l(l+1)(l+2)}}{2} \psi_{lm}.
\end{equation*}

@@
